\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\noindent This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the PoC demo and the Rev
0 demo; the contributions prior to the PoC are NOT included.

\section{Demo Plans}

We will demo one complete Proxi task from start to finish. The demo will show
how a user can give a natural-language command and Proxi can complete the
request end-to-end. Example tasks include actions related to messaging,
browsing, scheduling, and other everyday computer workflows.

The demo will follow these steps:
\begin{enumerate}
  \item Launch Proxi and show the UI is ready.
  \item Enter one command (voice or text).
  \item Show Proxi interprets the request and determines what to do.
  \item Show Proxi performs the action on the computer.
  \item Show the final confirmation and result in the UI.
\end{enumerate}


\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 9\\
Ajay Grewal & 9\\
Savinay Chhabra & 9\\
Amanbeer Singh Minhas & 9\\
Gourob Podder & 9\\
\bottomrule
\end{tabular}
\end{table}

\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: } This project has no supervisor \\
\noindent \textbf{Stakeholders: } Seniors

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 7\\
Ajay Grewal & 1\\
Savinay Chhabra & 3\\
Amanbeer Singh Minhas & 2\\
Gouroub Podder & 1\\
\bottomrule
\end{tabular}
\end{table}

Individual Team Members had chats with their grandparents and asked them questions
about their experiences during with their computing devices. These chats were 
informal and not scheduled meetings.

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Ajay Grewal & 1\\
Savinay Chhabra & 1\\
Amanbeer Singh Minhas & 1\\
Gourob Podder & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: } Christopher Schankula

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 0\\
Ajay Grewal & 0\\
Savinay Chhabra & 0\\
Amanbeer Singh Minhas & 0\\
Gouroub Podder & 0\\
\bottomrule
\end{tabular}
\end{table}

We had 1 TA meeting but it was cancelled due to a snow day.

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 127 & 100\% \\
Ajay Grewal & 39 & 30.7\% \\
Savinay Chhabra & 36 & 28.3\% \\
Amanbeer Singh Minhas & 25 & 19.7\% \\
Gouroub Podder & 27 & 21.3\% \\
\bottomrule
\end{tabular}
\end{table}

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Ajay Grewal & 3 & 1 \\
Savinay Chhabra & 3 & 1 \\
Amanbeer Singh Minhas & 3 & 1 \\
Gourob Podder & 3 & 0 \\
\bottomrule
\end{tabular}
\end{table}

\section{CICD}

Our project uses GitHub Actions to automate testing and documentation builds on
every update to the repository. For continuous integration, the \texttt{CI}
workflow is triggered on pushes and pull requests to \texttt{main},
\texttt{master}, and \texttt{develop}. It sets up a clean Ubuntu environment,
installs Python dependencies from \texttt{src/requirements.txt}, and runs the
full test suite with \texttt{pytest} on Python 3.11 and 3.12 to ensure
compatibility across versions. Test coverage is also checked using
\texttt{pytest-cov}, and the workflow reports missing coverage while allowing
the pipeline to continue so development is not blocked by coverage warnings.

\noindent For continuous delivery of documentation, we use a separate GitHub Actions
workflow called \texttt{buildtex} that triggers only when files under
\texttt{docs/} are changed on \texttt{main}. This workflow identifies which
\texttt{.tex} files were modified, compiles the corresponding PDFs using
\texttt{texlive-action}, and automatically commits and pushes the updated PDFs
back to the repository. This ensures the latest LaTeX documentation is always
kept up-to-date without requiring manual PDF compilation or uploads.


\section{Team Charter Trigger Items}

\textbf{Trigger Summary:} Based on our team charter, the primary triggers
for intervention include:
\begin{itemize}
  \item Missing a scheduled team or supervisor meeting without at least
        24 hours notice.
  \item Repeated missed deadlines or uncommunicated delays on assigned
        deliverables (more than 1--2 occurrences).
  \item Consistently arriving late to meetings without prior notice.
  \item Submitting low-quality or incomplete work without explanation.
  \item Disruptive behavior or conflict without attempting resolution
        through team discussion.
\end{itemize}

\noindent\textbf{Observed Trigger Events:} No formal trigger violations occurred
during this period. All absences or delays were communicated in advance and
approved by the team. Examples include:
\begin{itemize}
  \item One member joining late due to snow day.
  \item Another member briefly missing a work session to attend a lab but
        completing their assigned tasks later the same day.
  \item Short connectivity issues during one online meeting resolved within
        minutes.
\end{itemize}

All instances were communicated promptly and did not affect project progress
or deliverable quality.

\vspace{0.5em}
\noindent\textbf{Plan and Reflection:} No corrective actions were necessary as all
team members demonstrated responsibility and respect for deadlines and
communication. Moving forward, the team will:
\begin{itemize}
  \item Continue to provide early notice of scheduling conflicts.
  \item Balance academic workload and project responsibilities fairly.
  \item Maintain consistent participation and accountability.
\end{itemize}

Our current triggers remain appropriate and effective, requiring no revisions
at this stage.

\section{Additional Productivity Metrics}

To measure our overall progress and teamwork, the following simple
metrics were tracked during the period leading up to the POC demo:

\begin{itemize}
  \item \textbf{Meeting participation:} Each member attended over 90\%
        of team and supervisor meetings.
  \item \textbf{On-time submissions:} All major deliverables were submitted 
        before the deadline.
  \item \textbf{Peer review response time:} Feedback on documents was
        usually provided within 2 days.
\end{itemize}

\end{document}