% THIS DOCUMENT IS FOLLOWS THE VOLERE TEMPLATE BY Suzanne Robertson and James Robertson
% ONLY THE SECTION HEADINGS ARE PROVIDED
%
% Initial draft from https://github.com/Dieblich/volere
%
% Risks are removed because they are covered by the Hazard Analysis
\documentclass[12pt]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
      colorlinks=true,      % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

\newcommand{\lips}{\textit{Insert your content here.}}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Software Requirements Specification for \progname: subtitle describing software} 
\author{\authname}
\date{\today}
	
\maketitle

~\newpage

\pagenumbering{roman}

\tableofcontents

~\newpage

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\textbf{Date}} & {\textbf{Version}} & {\textbf{Notes}}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

~\\

~\newpage
\section{Purpose of the Project}
\subsection{User Business}
Proxi is an AI-powered desktop assistant that lets people operate a computer
entirely through natural speech. It targets users who face barriers with traditional
input devices (keyboard, mouse, complex UIs) and organizations that want to provide
inclusive access to essential digital tasks (communication, learning, work). Proxi
augments independence and reduces the digital divide by turning voice into safe,
precise computer actions. While accessibility is the primary driver, Proxi is
equally intended for general users who want faster, lower‑friction workflows so it
benefits both disabled and non‑disabled users.

\subsection{Goals of the Project}
\begin{description}
\item[G-1 (Latency)] Spoken system responses for common commands shall begin within 
$\leq$ 2.0 s from end-of-speech in a quiet environment.

\item[G-2 (Recognition Accuracy)] Command recognition accuracy for supported 
language(s) in quiet environment shall be $\geq$ 90\% intent-level accuracy.

\item[G-3 (Task Coverage)] Users from the primary user group shall complete $\geq$ 
80\% of a predefined core task suite (open app/file, browse, compose, save, 
schedule) using voice or keyboard.

\item[G-4 (Effectiveness)] Compared to baseline (traditional input for same users), 
Proxi shall improve task completion rate by $\geq$ 20\%.

\item[G-5 (Satisfaction)] Accessibility-focused usability tests shall yield 4.0/5.0 satisfaction score.

\item[G-6 (Stretch Goals)] Voice recognition improvements, offline capabilities, 
multimodal interaction support, personalized profiles, enhanced accessibility
\end{description}
\section{Stakeholders}
\subsection{Client}
The clients for this project are the SFWRENG 4G06A Capstone teaching team at 
McMaster University (course Instructor and assigned Teaching Assistants), serving 
as the product owners on behalf of the department. Their mandate is to ensure the 
solution meets accessibility, usability, and engineering quality standards 
appropriate for a capstone deliverable and potential real‑world piloting within 
academic environments. They provide domain expectations (accessibility best 
practices, privacy/compliance constraints in academic settings) and approve scope 
and milestones.
\subsection{Customer}
Our customers are the end-users and organizations that will deploy Proxi to enable 
inclusive and more efficient computer use:
\begin{itemize}
\item \textbf{Educational institutions} (libraries, computer labs, accessibility services) 
  seeking hands-free or low-friction access to standard desktops and web apps
\item \textbf{Healthcare and community organizations} supporting users with motor/vision/
  hearing challenges
\item \textbf{General consumers and power users} who prefer faster, voice-first or mixed-
  modality workflows

\end{itemize}

\subsection{Other Stakeholders}
Other stakeholders include any person or group with interest beyond the client and 
the customer:
\begin{itemize}
\item \textbf{Team Proxi (development team):} responsible for requirements, design, 
  implementation, testing, and deployment artefacts
\item \textbf{Course Staff (Instructor \& TA):} guidance, assessment, feedback, and 
  approvals
\item \textbf{Accessibility Advisors (if engaged):} best practices for WCAG/AT compatibility
\item \textbf{Pilot participants:} individuals who will use the system during user studies 
  and provide feedback
\end{itemize}
\subsection{Hands-On Users of the Project}
Primary hands-on users who will directly interact with Proxi:
\begin{itemize}
\item \textbf{Accessibility-focused users:} People with motor impairments or 
  temporary/situational limitations needing hands-free or simplified control
\item \textbf{General users/power users:} Users seeking faster workflows via 
  voice/text commands with optional keyboard/mouse confirmation
\end{itemize}
\subsection{Personas}
\begin{itemize}
\item \textbf{P1: Amrita (72) - Elderly User:} Amrita is a retired teacher who uses her desktop to 
check emails, pay bills, and video call her family. She struggles with small buttons, 
complicated menus, and remembering multi-step actions, which makes her anxious about 
using technology. She needs a way to perform common tasks more easily and with clear 
guidance to feel confident online.

\item \textbf{P2: Leo (21) - User with Motor Disability:} Leo is a computer science student who finds
it difficult to use a keyboard or mouse due to a motor impairment. He needs to read PDFs,
take notes, and switch between different apps for his coursework. He requires a way to 
interact with his computer hands-free and complete his work without relying on physical 
input.

\item \textbf{P3: Ari (28) - Power User:} Ari works with spreadsheets, emails, and web tools 
throughout the day and often repeats the same steps over and over. Switching between 
programs slows him down, and remembering different commands and shortcuts is frustrating. 
He needs a more efficient way to complete multi-step tasks and manage his work without 
constant interruptions.
\end{itemize}
\subsection{Priorities Assigned to Users}
The \textbf{highest priority} users for this project are \textbf{accessibility-focused} users, 
including elderly users like Amrita and users with motor impairments like Leo, as 
the main goal is to improve computer access and usability for people who face 
physical challenges or find current systems difficult to use. Their needs guide 
the core features and design decisions of the project. \textbf{Power users} like Ari are 
the \textbf{secondary priority} because, while they do not face accessibility barriers, 
their focus on speed and efficiency helps shape advanced features that make the 
system useful to a wider audience. Prioritizing these groups ensures the solution 
is both inclusive for those who need accessibility support and valuable for 
everyday users seeking more efficient workflows.
\subsection{User Participation}
Estimated participation during the project will primarily involve end users and the
development team. Accessibility-focused users are expected to participate for about 1
hour per week through remote or in-lab sessions focused on usability testing,
feedback, and formative evaluations. General users and power users will contribute
roughly 1 hour per week by taking part in efficiency and performance testing of new
features. Additionally, the development team will dedicate around 8–10 hours per week
to designing, building, testing, and refining the system based on user feedback and
project milestones.
\subsection{Maintenance Users and Service Technicians}
The primary maintenance users for this project will be the development team. During the
capstone project, they will be responsible for identifying and fixing issues, releasing 
updates and patches, and ensuring that the system continues to function as expected throughout 
development. They will also create and maintain documentation such as installation guides and
user manuals to support future use and potential handoff of the project after completion.

\section{Mandated Constraints}
\subsection{Solution Constraints}
\lips
\subsection{Implementation Environment of the Current System}
\lips
\subsection{Partner or Collaborative Applications}
\lips
\subsection{Off-the-Shelf Software}
\lips
\subsection{Anticipated Workplace Environment}
\lips
\subsection{Schedule Constraints}
\lips
\subsection{Budget Constraints}
\lips
\subsection{Enterprise Constraints}
\lips

\section{Naming Conventions and Terminology}
\subsection{Glossary of All Terms, Including Acronyms, Used by Stakeholders
involved in the Project}
\begin{description}
  \item[MCP (Model Context Protocol)] A contract with which an AI agent can find 
  and invoke a toolset to accomplish specific tasks.

  \item[MCP Server] A local server that implements the MCP to allow AI agents
  to discover and use the available tools.

  \item[MCP Client] An AI agent that connects to the MCP server to use the provided tools.

  \item[AI Agent] A software (LLM) that uses artificial intelligence to perform tasks.

  \item[LLM (Large Language Model)] A type of AI model that can understand and
  generate human language.

  \item[Token] A unit of text used in LLMs to process and generate language.

  \item[Sandbox] A secure environment in which code can be run and tested without
  affecting the rest of the system.

  \item[Action] A single execution of a tool with validated parameters.

  \item[Plan] An ordered sequence of actions to fulfill a user intent.

  \item[Command] An instruction given by the user to the AI agent.

  \item[Permission Scope] Level of access that is given to the AI agent for completing actions.

  \item[Confirmation Gate] A approval prompt given to the user by the AI before cpmpleting
  risky actions.

  \item[TTS (Text-to-Speech)] Tool that converts written text into spoken words.

  \item[STT (Speech-to-Text)] Tool that converts spoken words into written text.

  \item[Audit Log] A record of all actions taken by the AI agent.

  \item[Accessibility] It is usable by people with a wide range of abilities/disabilities.

  \item[User Interface (UI)] The visual elements of the software (frontend) in which a user will engage with the system.

  \item[PII (Personally Identifiable Information)] Any data that could identify a specific individual.

  \item[POLP (Principle of Least Privilege)] A security concept in which the AI agent will have minimum levels of access 
  necessary to perform certain tasks.

  \item[OS Automation Tools] Software on one's computer that gives the AI agent the ability to control and engage with their OS.
\end{description}

\section{Relevant Facts And Assumptions}
\subsection{Relevant Facts}
\lips
\subsection{Business Rules}
\lips
\subsection{Assumptions}
\lips

\section{The Scope of the Work}
\subsection{The Current Situation}
\lips
\subsection{The Context of the Work}
\lips
\subsection{Work Partitioning}
\lips
\subsection{Specifying a Business Use Case (BUC)}
\lips

\section{Business Data Model and Data Dictionary}
\subsection{Business Data Model}
\lips
\subsection{Data Dictionary}
\lips

\section{The Scope of the Product}
\subsection{Product Boundary}
\lips
\subsection{Product Use Case Table}
\lips
\subsection{Individual Product Use Cases (PUC's)}
\lips

\section{Functional Requirements}
\subsection{Functional Requirements}
\lips

\section{Look and Feel Requirements}

\subsection{Appearance Requirements}

\begin{description}
  \item[APP.1] The interface should look simple and familiar, like a normal 
  desktop tool with a small status bar that shows when the system is 
  listening, thinking, or ready.
  
  \item[APP.2] Main actions such as listen, stop, undo, and confirm should 
  be clearly visible as buttons on the main screen.
  
  \item[APP.3] The screen should not feel crowded; only the most important 
  options should be shown, and advanced options hidden in a simple menu.
  
  \item[APP.4] Text and buttons should be large and easy to read or click, 
  especially for new or elderly users.
  
  \item[APP.5] A light and dark theme toggle should be available so users 
  can choose what is most comfortable for them.
\end{description}

\subsection{Style Requirements}

\begin{description}
  \item[STY.1] Labels and messages should use short, plain language with no 
  technical hard language.
  
  \item[STY.2] When the system speaks, the text should also appear on 
  screen as captions.
  
  \item[STY.3] Icons should stay consistent and have a short text label 
  underneath to avoid confusion.
\end{description}

\section{Usability and Humanity Requirements}

\subsection{Ease of Use Requirements}

\begin{itemize}
  \item \textbf{EOU.R.1} The system shall be easy for new users to start using. 
  Basic tasks like opening an application or reading a file should require only 
  one simple command or button press.

  \item \textbf{EOU.R.2} The system shall have an intuitive interface that does 
  not overwhelm users. Main actions such as listen, stop, undo, and confirm 
  must be clearly visible and easy to access.

  \item \textbf{EOU.R.3} After a short introduction, users should be able to 
  complete most everyday tasks without assistance, and tasks should become 
  faster with practice.
\end{itemize}

\subsection{Personalization and Internationalization Requirements}

\begin{itemize}
  \item \textbf{PER.R.1} The system shall adapt to a user's speech patterns over 
  time to improve recognition accuracy.

  \item \textbf{PER.R.2} The system shall support Canadian English standards 
  for language, date, and time formatting and allow future translation if needed.
\end{itemize}

\subsection{Learning Requirements}

\begin{itemize}
  \item \textbf{LEA.R.1} The system shall have a short learning curve, allowing 
  new users to understand and use basic commands within 30 minutes.

  \item \textbf{LEA.R.2} The system shall provide a list of example commands 
  or a ``what can I say'' option to help users learn available features quickly.
\end{itemize}

\subsection{Understandability and Politeness Requirements}

\begin{itemize}
  \item \textbf{UAP.R.1} The system shall use simple and clear language for all 
  text and messages, avoiding technical jargon.

  \item \textbf{UAP.R.2} The system shall confirm actions that could change or 
  delete important files or settings before executing them.

  \item \textbf{UAP.R.3} Error messages shall be polite, explain the issue in 
  plain language, and suggest a next step to fix it.
\end{itemize}

\subsection{Accessibility Requirements}

\begin{itemize}
  \item \textbf{ACC.R.1} The system shall allow all actions, including setup and 
  exit, to be performed using voice commands without requiring a keyboard 
  or mouse.

  \item \textbf{ACC.R.2} The system shall comply with recognized accessibility 
  standards such as \textbf{WCAG 2.2} and the \textbf{Accessibility for Ontarians 
  with Disabilities Act (AODA)}. All interface elements must provide captions for 
  spoken responses, support text scaling, and ensure sufficient color contrast to 
  assist users with visual impairments.
\end{itemize}


\section{Performance Requirements}

\subsection{Speed and Latency Requirements}

\begin{itemize}
  \item \textbf{SAL.R.1} The system shall begin responding to a voice command 
  within 2 seconds under normal conditions.
  
  \item \textbf{SAL.R.2} Common actions, such as opening an application or 
  navigating files, shall complete within 3 seconds on standard hardware.
\end{itemize}

\subsection{Safety-Critical Requirements}

\begin{itemize}
  \item \textbf{SAF.R.1} Any action that changes files or system settings shall 
  require user confirmation before execution.
  
  \item \textbf{SAF.R.2} The system shall allow users to undo or roll back 
  critical actions in a single step to prevent accidental changes.
\end{itemize}

\subsection{Precision or Accuracy Requirements}

\begin{itemize}
  \item \textbf{POA.R.1} The system shall correctly recognize at least 90\% of 
  supported voice commands in a quiet environment.
  
  \item \textbf{POA.R.2} In a moderately noisy environment, the system shall 
  maintain at least 80\% command recognition accuracy.
\end{itemize}

\subsection{Robustness or Fault-Tolerance Requirements}

\begin{itemize}
  \item \textbf{ROFT.R.1} The system shall log and report input errors without 
  crashing or losing user data.
  
  \item \textbf{ROFT.R.2} The system shall continue running even if it receives 
  an invalid or incomplete command.
\end{itemize}

\subsection{Capacity Requirements}

\begin{itemize}
  \item \textbf{CAP.R.1} The system shall support continuous operation for at 
  least 4 hours without performance degradation.
  
  \item \textbf{CAP.R.2} CPU usage shall remain under 30\% during normal 
  operation on standard hardware.
\end{itemize}

\subsection{Scalability or Extensibility Requirements}

\begin{itemize}
  \item \textbf{SOE.R.1} The system shall allow new features or modules to be 
  added without major changes to existing functionality.
  
  \item \textbf{SOE.R.2} Any new feature or skill shall load and become 
  available for use within 200 milliseconds.
\end{itemize}

\subsection{Longevity Requirements}

\begin{itemize}
  \item \textbf{LON.R.1} The system shall retain all user settings and 
  personalization data after updates.
  
  \item \textbf{LON.R.2} The system shall allow rollback to a previous version 
  within 60 seconds if an update fails.
\end{itemize}


\section{Operational and Environmental Requirements}
\subsection{Expected Physical Environment}
\lips
\subsection{Wider Environment Requirements}
\lips
\subsection{Requirements for Interfacing with Adjacent Systems}
\lips
\subsection{Productization Requirements}
\lips
\subsection{Release Requirements}
\lips

\section{Maintainability and Support Requirements}
\subsection{Maintenance Requirements}
\lips
\subsection{Supportability Requirements}
\lips
\subsection{Adaptability Requirements}
\lips

\section{Security Requirements}
\subsection{Access Requirements}
\lips
\subsection{Integrity Requirements}
\lips
\subsection{Privacy Requirements}
\lips
\subsection{Audit Requirements}
\lips
\subsection{Immunity Requirements}
\lips

\section{Cultural Requirements}
\subsection{Cultural Requirements}
\lips

\section{Compliance Requirements}
\subsection{Legal Requirements}
\lips
\subsection{Standards Compliance Requirements}
\lips

\section{Open Issues}

\begin{itemize}
  \item \textbf{OI.1} The integration of the MCP (Model Context Protocol) for 
  controlling system-level functions is still in progress, and further testing is 
  needed to ensure reliable and safe execution of commands across different 
  applications.

  \item \textbf{OI.2} The system’s compatibility and consistent performance 
  across different operating systems (such as Windows, macOS, and Linux) 
  have not yet been fully tested or confirmed.

  \item \textbf{OI.3} Ensuring that user commands do not unintentionally trigger 
  harmful or unauthorized actions on the device is still under investigation 
  and requires additional safety checks and permission handling.
\end{itemize}


\section{Off-the-Shelf Solutions}
\subsection{Ready-Made Products}
\lips
\subsection{Reusable Components}
\lips
\subsection{Products That Can Be Copied}
\lips

\section{New Problems}
\subsection{Effects on the Current Environment}
\lips
\subsection{Effects on the Installed Systems}
\lips
\subsection{Potential User Problems}
\lips
\subsection{Limitations in the Anticipated Implementation Environment That May
Inhibit the New Product}
\lips
\subsection{Follow-Up Problems}
\lips

\section{Tasks}
\subsection{Project Planning}
\lips
\subsection{Planning of the Development Phases}
\lips

\section{Migration to the New Product}
\subsection{Requirements for Migration to the New Product}
\lips
\subsection{Data That Has to be Modified or Translated for the New System}
\lips

\section{Costs}
\lips
\section{User Documentation and Training}
\subsection{User Documentation Requirements}
\lips
\subsection{Training Requirements}
\lips

\section{Waiting Room}
\lips

\section{Ideas for Solution}
\lips

\newpage{}
\section*{Appendix --- Reflection}

\input{../Reflection.tex}

\input{../SRS_Reflection.tex}

\end{document}